\documentclass[12pt]{article}
\usepackage{verbatim, amsfonts, amsmath, amssymb, hyperref,enumerate,multicol}
\pagestyle{empty}
\voffset=-.5in
\textheight=8.75in
\textwidth=6in
\hoffset=-.35in

\newcommand{\ls}{\vspace{.1in}}
\newcommand{\ds}{\displaystyle}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}



\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Math Foundations}
\rhead{Written HW 3}
\cfoot{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\begin{document}

\centerline{\bf Written Homework 3}


\centerline{Name(s): Elliot Marshall}
\begin{enumerate}
\item[3.1.10.] Determine if each of the following propositions is true or false.  Justify each conclusion.
\begin{enumerate}
\item[b.] True. For each integer $a$, if $a\equiv 2 \mod 8$, then $a^2\equiv 4 \mod 8$.
\par let $a\,\epsilon\,\Z $ and $a \equiv 2 \mod 8$, then $8\,|\, a - 2$. Since 
$n|m\rightarrow n|ml$ for some $n,m,l\,\epsilon\,\Z$, then $\exists\,n$ S.T. 
$n=(a-2)*(a+2) = (a^2-2^2) = (a^2-4)\equiv\,4\mod 8$.
\item[c.] For each integer $a$, if $a^2\equiv 4 \mod 8$, then $a\equiv 2 \mod 8$.
\par False. There are a total of 8 cases for a: $a = \{0,1,2,3,4,5,6,7\}$. The one case 
that fufills the premis but not the conclusion is when $a = 6 $. $\therefore 
a^2 = 36 \rightarrow 36\mod8\equiv4$ but $6\mod8\equiv6\not\equiv2$
\end{enumerate}

\hrulefill


\item[3.2.10.] Is the following proposition true or false?  Justify.
\begin{quote} For each integer $n$, $n$ is even if and only if 4 divides $n^2$.
\end{quote}
\par True.\\
% establish integer exponentiation as multiplication
First, since integer exponentiation is the equivalent of repetitive multiplication, $n^2 = n*n$.
% odd integers must square to odd numbers
Second, odd numbers square to odd numbers: let $x$ be an odd integer, then by defination, $x = 
2k+1, k\epsilon\Z$. Then: \begin{center} $x^2 = (2k+1)^2$\\$=4k^2+4k+1$\\$=2(2k^2+2k)+1$
\\$=2j+1$\end{center} Where $j\,\epsilon\,\Z$ since integers are closed under addition and 
multiplication and therefore $x^2$ is odd.\\
% if 4 divides n^2 then 2 must divide n^2
If $4\,|\,n^2$, then $2\,|\,n^2$ since $2|4$ and $n|m\rightarrow n|ml$ for some $n,m,l\,\epsilon
\,\Z$


%If $4|n^2$, then $2|n^2$ since $n|m\rightarrow n|ml$ for some $n,m,l\,\epsilon\,\Z$ and since 
%$n\,\epsilon \,\Z$ and integers are closed under multiplication $(n*n = n^2)$, $n^2$ is 
%an even integer. Since an odd integer squared is equivalent to $(2*k+1)^2 = (4k^2+4k+1) = 
%(2*(2k^2+2k)+1) = 2j+1,$ and $j\epsilon\Z$ because integers are closed under multiplication 
%and addition, the square of an odd integer must be an odd integer. Therefore, since $n^2\,
%\epsilon\,\Z$ and even integers take the form of |

\hrulefill


\item[3.3.6.]  Are the following statements true or false?  Justify.
\begin{enumerate}
\item[c.] For every pair of real numbers $x$ and $y$, if $x+y$ is irrational, then $x$ is irrational and $y$ is irrational.
\item[d.] For every pair of real numbers $x$ and $y$, if $x+y$ is irrational, then $x$ is irrational or $y$ is irrational.
\end{enumerate}

\hrulefill

\item[3.4.7.] Is the following proposition true or false?  Justify your conclusion with a counterexample or a proof.
\begin{quote} For each integer $n$, if $n$ is odd, then $8|(n^2-1)$.
\end{quote}


\end{enumerate}



\end{document}